Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-03-27 paper/paper.tex
Figures description
Sketch LB

@@

>>>>

\maciek{Figure: cluster types}

\maciek{Figure: an unsaturated edge that is inside a component}

@@

\section{Lower bound $2k-1$ for two clusters}

\maciek{Sketch only}

We reduce the paging problem with the universe $U$ of size $2k$ and the cache of size $2k-1$.
Recall that the lower bound for the competitive ratio for such paging problem is $2k-1$.

We partition nodes into $3$ sets: $A$, $B$ and $C$.
Sets has the following cardinality: $|A| = k-1$, $|B| = k-1$, and $|C| = 2$.
We arbitratry assign all elements of the universe $U$ to nodes from $A\cup B\cup C$.
Note that in every configuration, at least one of these sets is split, i.e., is not completely contained in one cluster.
